Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
new proposal for the title
set author given discussion

\title[Inference of connectomes using partial correlation coefficients]{Simple and robust inference of connectomes using partial correlation coefficients}

@@

 % Three or more authors with the same address:
 \author{Todo authors}

%% Proposition (sujet à changements : on en discutera):
% Antonio
% {Aaron, Arnaud, Vincent} : aucune préférence pour ma part
% Gilles
% Damien?
% Pierre?

>>>>

% \title[Inference of connectomes using partial correlation coefficients]{Simple and robust inference of connectomes using partial correlation coefficients}

\title{Connectome inferences using partial correlation from imaging calcium signal}

@@

 % Three or more authors with the same address:
 % \author{ Antonio Sutera %\and
 %         % \Name{Arnaud Joly} \and
 %         % \Name{Vincent Fran\c{c}ois-Lavet} \and
 %         % \Name{Aaron Qiu} \and
 %         % \Name{Gilles Louppes} \and
 %         % \Name{Damien Ernst} \and
 %         % \name{Pierre Geurts}}
 %         }
\author{Antonio Sutera,
        Arnaud Joly,
        Vincent François-Lavet,
        Aaron Qiu, \\
        Gilles Louppes,
        Damien Ernst,
        Pierre Geurts}
